% ************************** Thesis Acknowledgements **************************

\chapter*{Acknowledgements}
% \setlength{\epigraphwidth}{0.5\textwidth}
% \epigraph{\centering\textit{A tutti (scusate se dimentico qualcuno):\\\ldots  grazie.}}{}

\dedicatory{A tutti (scusate se dimentico qualcuno):\\\ldots grazie.}

% Andre, Francesco, Dani, Ale Saccon 

The first group of people I would like to thank are the one that I consider my ``scientific mentors'', the one without which this thesis simply would not exists. The first one is Andrea Del Prete, that I first met during my Master's studies, and with which I had the luck of working while preparing my Master's Thesis and before starting my PhD. The second one is Francesco Nori, my Master's and PhD supervisor and the first person in my professional life to trust me with real responsibility. The third one is Daniele Pucci, that was an invaluable companion during my PhD. The fourth one is Alessandro Saccon that I visited in Eindhoven during the end of 2015, and with which I had a lot ``open-minding'' discussions. 

I would like to thank also all my other colleagues at the Istituto Italiano di Tecnologia (IIT), firstly Francesco (Romano), Johrabib and Luca with whom I had the lucky to start to work in the group that would later become the Dynamic Interaction Control group at IIT. Furthermore, I would like to thank all other people that joined the Dynamic Interaction Control lab at different stages and in different ways: Talha, Naveen, Francesca, Yue, Prashanth, Claudia, Nuno, Gabriele, Francisco, Marie, Stefano, Matteo, Ali, Joan, Marta, Maria and Diego. Your feedback, even when just asking question, was invaluable for this thesis. 

I would also like to thanks are the amazing crew that before I joined IIT and during the years built and maintained the iCub robot and all the related infrastructure. Ugo, Randaz, Vadim, Lorenzo, Daniele, Ali, Giorgio, Maggia, Stefano, Alberto, Marco, Valentina, Julien, Spada, Gesino, Masa, Marcello were for me an example of dedication. Trying to be at their level has always been a great motivation to always learn more and work harder. 

I would like to thank who in this years took care that I was coming to work everyday: Francesco, Raffaello and Cive when commuting by car, and Anand, Giovanni and Emy when living in Genoa. 

% Cohousing 

% Benni, Titti, One 

% Santo Stefano Del Ponte  

% Family 

I would like to thank Benni, Titti and One. I would also like to thank the parish I have grown up in, Santo Stefano del Ponte, and everyone I met related to that. All those experiences thought me the few things I know about trying to care for any human being, a fundamental skill for any job. I would also like to thank my family, my sister Marta, my parents Caterina and Gian Renzo, my aunt Anna and my grandparents Angelina, Guido, Olga and Silvio. In the deepest sense, this thesis would have never been written if it was not for them.

Last, I would like to thank Camilla (or \emph{Cami}, as she prefers to be called). The kind of gratitude I have towards her is simply not fit to print in this thesis.

% Camilla 

